Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-20 paper_quarto.qmd
reference added

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Lizao Zhuang (Dawn) r0914937"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
code-fold: true
bibliography:
  - bibliography.bib
  - packages.bib
csl: unified-style-sheet-for-linguistics.csl
abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
---

@@

`{tidyverse}`, `{mclm}` are the main packages used in this paper.

@@

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
:::

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "`r (Signed G^2^)`"))%>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

```{quarto-cite}
```

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Lizao Zhuang (Dawn) r0914937"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
code-fold: true
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
---

@@

[@R-tidyverse] and [@R-mclm] [@R-base] [@R-ggplot2] [@R-leaflet] are the main packages used in this paper. [@dodd2021] [@nappo2017]

@@

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
:::

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

Trade related words (including important transportation milestones, trading goods and the description of the goods (colors, precious, etc.)) are more prone to be occur in the text related to India. It reflects the trading connection of the two empires, and also how the recognition of the other empire for the scholars of that period.
